Analysis paper

### 2021-06-15 analysis/analysis.Rmd
update plots

  filename <- here("analysis", "plots", 
                   paste0("truth-and-", horizon, "-wk-ahead_cases"))
  ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_cases)

@@

# create helper function to plot forecasts -------------------------------------
scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
  p <- scores %>%
  ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
  geom_line(aes(colour = model)) + 
  geom_point(aes(shape = classification, colour = model)) + 
  theme_light() + 
  facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
  theme(legend.position = "bottom") +
  # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
  #               xmax = max(forecast_dates$christmas) + 14,
  #               ymin = 0,
  #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
  # theme(panel.background = element_rect(fill = "#e1f0fe")) +
  # scale_y_log10() + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

>>>>

  filename <- here("analysis", "plots", 
                   paste0("truth-and-", i, "-wk-ahead_cases"))
  ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_cases)

@@

# create helper function to plot forecasts -------------------------------------
scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
  p <- scores %>%
  ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
  geom_line(aes(colour = model)) + 
  geom_point(aes(shape = classification, colour = model)) + 
  theme_light() + 
  facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
  theme(legend.position = "bottom") +
  # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
  #               xmax = max(forecast_dates$christmas) + 14,
  #               ymin = 0,
  #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
  # theme(panel.background = element_rect(fill = "#e1f0fe")) +
  # scale_y_log10() + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}
